### 2012-02-21 tr-semanticsearchsurvey-data/intro.tex

Likewise, research interest in semantic search is stirring up. A large body of work has been proposed by researchers from different communities, including database, Information Retrieval (IR) and Semantic Web. Correspondingly, semantic search has been viewed from different angles, resulting in a plethora of solutions. While underlying all these efforts lie one central idea, namely to use semantic resource for more effective search, existing approaches greatly vary in the information needs, the query and the data that are supported. Hence, different concepts and techniques have been studied in these settings. Most notably, there are principle differences between semantic search approaches, which use semantic resource to improve document retrieval, and the ones that compute direct results, i.e. \emph{semantic data retrieval}.

@@

\begin{itemize}
	\item In this work, we present a systematic survey to provide a \emph{taxonomy of various semantic search approaches}, to reflect on the achievements that have been made over these years, and finally, to discuss the remaining challenges and directions for future research. To the best of our knowledge, the only work... 
	\item Besides this general overview, we discuss the \emph{state-of-the-art in semantic data retrieval}, a direction of semantic search that aims at direct results as answers. For this, different data management and processing tasks are needed, from the crawling and integration of data up to the computation and presentation of results. 
	\item We present specific solutions that have been proposed for these individual tasks. Particular emphasis is put on the most commonly used interface, namely \emph{keyword search}, and the concepts and techniques for dealing with the core search tasks of \emph{matching and ranking}.

>>>>

Likewise, research interest in semantic search is stirring up. A large body of work has been proposed by researchers from different communities, including database, Information Retrieval (IR) and Semantic Web. Correspondingly, semantic search has been viewed from different angles, resulting in a plethora of solutions. While underlying all these efforts lie one central idea, namely to use semantic resource for more effective search, existing approaches greatly vary in the information needs, the query and the data that are supported. Hence, different concepts and techniques have been studied in these settings. Most notably, there are principle differences between semantic search approaches, which use semantic resource to improve \emph{document retrieval}, and the ones that compute direct results, i.e. semantic \emph{data retrieval}.

@@

\begin{itemize}
	\item In this work, we present a systematic survey to provide a \emph{taxonomy of various semantic search approaches}, to reflect on the achievements that have been made over these years, and finally, to discuss the remaining challenges and directions for future research. To the best of our knowledge, the only work... 
%	\item Besides this general overview, we discuss the \emph{state-of-the-art in semantic data retrieval}, a direction of semantic search that aims at direct results as answers. For this, different data management and processing tasks are needed, from the crawling and integration of data up to the computation and presentation of results. 
%	\item We present specific solutions that have been proposed for these individual tasks. Particular emphasis is put on the most commonly used interface, namely \emph{keyword search}, and the concepts and techniques for dealing with the core search tasks of \emph{matching and ranking}.
